\vspace*{-10pt}
\sectionTitle{Experience}{\faSuitcase}
\begin{experiences}
\experience{}{Java Software Engineer}{Avan Software Technology Advisors (ASTA)}{Tehran, Iran {\scriptsize{(Remote)}}. 
\hspace{20 pt} January 2024 - Peresent }{}
{
  Avan Software Technology Advisors (\emph{ASTA}) was founded in 2003 with the mission to deliver IT solutions to a wide range of enterprises in the public sector. In this company, I was working on an \href{https://github.com/flickit-platform/flickit-assessment}{open-source} project named \href{https://flickit.org/}{Flickit}.
  \begin{itemize}
    \item Spearheaded the development of RESTful and microservices-based APIs, leveraging Java 17, \emph{Spring Boot} technologies and hexagonal architecture.
    \item Collaborated within a midsize team to integrate \emph{Minio} storage solutions and \emph{PostgreSQL} database, enhancing data management capabilities while adhering to Test-Driven Development (TDD) practices and promoting clean code standards. \end{itemize}}
  {Microservice, Kubernetes, Scrum, Linux, Clean Code, Clean Architecture, BDD, JUnit, Mockito, Elastic Search, Logstash} 
 \emptySeparator
 \experience{}{Senior Java and Clojure Developer}{\href{https://epfccorp.com/}{EPFC}}{Calgary, Canada {\scriptsize{(Remote)}}. \hspace{110 pt} July 2022 - December 2023 }{}
 {
   \emph{EPFC} is a diverse team of professionals with extensive experience in engineering, procurement, fabrication, construction, commission and start-up, and operations in oil and gas. We developed an ERP system as part of the IT team to facilitate company procedures.
   \begin{itemize}
   \item Engaged with 50 developers and experts using \emph{Scrum} and \emph{DDD} to investigate the \textit{ERP} web app's domain and boundaries.
   \item Employed the \emph{Clojure} programming language and followed the \emph{TDD} process and \textit{CQRS} principle for 27 \emph{microservices}.
   \item Employed the \textit{event sourcing} principle, \textit{Simple Queuing Service (SQS)} and \textit{Simple Notification Service (SNS)} interacting with the microservices.
   \item Collaborated with the DevOps team in terms of automation and Bash scripting to achieve more than 30 percent, speeding up the deployment procedure.
   \end{itemize}}{Domain-Driven Design, Test-Driven Development, AWS, PostgreSQL, Docker, Kanban, Linux, Pair Programming, CQRS, CI/CD}
  \emptySeparator 
\experience
{}
{Java Developer}
{\href{https://raadpardaz.ir/}{Radpardaz Razi}}
{Kermanshah, Iran {\scriptsize{(Remote)}}. \hspace{150 pt} January 2020 - June 2022}
{}
{
\par{Radpardaz Razi operates within the security IT industry, specializing in enhancing the security of existing applications and developing new ones.}
\begin{itemize}
\item Managed the creation of a sizable \emph{ERP} web app, employing \emph{Spring Boot} to interface with \emph{Apereo CAS} as a client.
\item Formulated protocols (\emph{SAML}, \emph{CAS}, and \emph{OAuth 2.0}) to define a secure path to interact services with the \textit{CAS}.
\item Managed users' authentication information, including over 20,000 users, using \emph{OpenLDAP} and \emph{Active Directory}
\end{itemize}
}{Central Authentication System, Single Sign in Single Sign out (SSO), Tomcat, Gradle, Hibernate, MVC, REST API, Bash Script, Linux, Scrum}
\emptySeparator
\experience
  {}
  {Android Developer}
  {\href{https://www.spotbar.ir/}{SPOT online taxi}}
  {Kermanshah, Iran. \hspace{140 pt} September 2017 - May 2019}
  {}
  {
  SPOT is a prominent online taxi service with a user base exceeding 100,000 in Iran. 
  \begin{itemize}
    \item In a sub-20 member team, aided Android taxi app development using Java.
    \item Employed Google Map's \emph{Geolocation}, \emph{Geocode}, and \emph{Reverse Geocode} APIs for navigation.\end{itemize}
  }{Java, Android Studio, JUnit, MVC, JDBC, SQLite, SQL, Google Map Platform}

\emptySeparator

\experience
{}
{Android Developer}
{Islamic Azad University incubator}
{Kermanshah, Iran. \hspace{60 pt} September 2015 - July 2017}
{}
{
\begin{itemize}
\item Collaborated as a Java developer with three teams, consisting of over 10 developers, in successfully setting up 3 startups including two social media app.
\item Crafted a dual-tier cache with \emph{SharedPreference} API and \emph{SQLite} database for 1000+ records from a \emph{MySQL} database.
\item Built 2 rich social media applications and ensured their API security using the \emph{JWT} token.
\end{itemize}
}{Java, Android Studio, JUnit, MVC, JDBC, JWT, MySQL, SQLite, cPanel}
\end{experiences}