%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Java Software Engineer} % Job title
    {\href{https://asta.ir/}{AVAN Software Technology Advisors (ASTA)}} % Organization
    {Tehran, Iran (Remote)} % Location
    {Jan 2024 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item Developed and maintained 8+ microservices for the \href{https://github.com/flickit-platform}{\textit{open-source}} \href{https://www.flickit.org}{Flickit} project using \textit{Java 21}, \textit{Spring Boot}, and \textit{hexagonal architecture}.
        \item Integrated \textit{MinIO} and \textit{PostgreSQL}, enhancing data handling efficiency by 20\%, improving storage and retrieval.
        \item Ensured Clean Code and \textit{TDD} compliance across 10,000+ lines of production code to ensure maintainable and adaptable software.
        \item Developed and maintained \textit{Backend-for-Frontend} (BFF) layer in \textit{Python} to streamline frontend integration.
        \item Configured and customized \textit{Keycloak} and integrated it with \textit{Spring Boot} (OAuth2/OIDC, JWT, role-based access control), implementing centralized authentication, SSO across services, and fine-grained authorization policies to strengthen security.
        \item Contributed to the \href{https://refahyar.ir}{Refahyār} fintech platform by developing a high-performance credit gateway and aggregator, enabling secure credit validation and scalable partner integration.
        \item Implemented Redis-based caching and rate-limiting mechanisms to enhance system performance, reduce database load, and ensure reliable request throttling.
        \item Transitioned from synchronous REST APIs to an asynchronous event-driven architecture using \textit{Apache Kafka}, decoupling core microservices and improving system resilience and scalability.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Java \& Clojure Developer} % Job title
    {\href{https://www.epfccorp.com/}{EPFC Corp.}}  % Organization
    {Calgary, Canada (Remote)} % Location
    {Jul 2022 -- Dec 2023} % Date(s)
    {
      \begin{cvitems}
        \item Partnered with 50+ engineers and business stakeholders to develop a large-scale ERP system using \textit{Domain-Driven Design} (DDD) and \textit{Scrum}, establishing clear business domains and improving cross-team alignment.
        \item Engineered 27 microservices using \textit{Clojure}, \textit{CQRS}, and \textit{Test-Driven Development} (TDD), ensuring scalability and code quality.
        \item Boosted API responsiveness by 30\% by implementing \textit{Amazon SQS}, \textit{SNS}, and \textit{event sourcing}, improving system efficiency and scalability.
        \item Coordinated the automating the \textit{CI/CD} pipeline, reducing deployment time by 32\% and enhancing release reliability.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Java Developer} % Job title
    {Radpardaz Razi} % Organization
    {Kermanshah, Iran} % Location
    {Jan 2020 -- Jun 2022} % Date(s)
    {
      \begin{cvitems}
        \item Developed a modular, microservices-based architecture for the \textit{ERP} system with \textit{Spring Boot}, enhancing system scalability and reducing deployment time by 40\% across 10+ services
        \item Designed authentication protocols (\textit{SAML}, \textit{CAS}, \textit{OAuth2}) and managed access for 20,000+ users via \textit{OpenLDAP} and \textit{Active Directory}.
        \item Automated application deployment across 8 servers using \textit{CI/CD} pipelines, ensuring consistent delivery.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Android Developer} % Job title
    {SPOT Online Taxi} % Organization
    {Kermanshah, Iran} % Location
    {Sep 2017 -- May 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Developed an Android app with real-time map and location APIs, reducing delivery times by 40\% and improving user experience.
        \item Integrated \textit{Google Maps Geolocation}, \textit{Geocode}, and \textit{Reverse Geocode} APIs into the navigation system, achieving a 40\% reduction in average delivery time through real-time route optimization and traffic analysis.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Android Developer} % Job title
    {Islamic Azad University Incubator} % Organization
    {Kermanshah, Iran} % Location
    {Sep 2015 -- Jul 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Led development efforts in 3 startup teams in launching social media apps, utilizing \textit{Java} and \textit{JWT}-based API security for robust authentication.
        \item Implemented a two-tier cache system with \textit{Shared Preferences} and \textit{SQLite}, boosting data retrieval and app performance by 20\%.
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
