\sectionTitle{Experience}{\faSuitcase}
\begin{experiences}
\experience{}{Java and Clojure Developer}{RDSysCo}{Iran, Isfahan December \hspace{160 pt} July 2022 - Present }{}
{
  \linkedin{rdsysco}
  \website{https://epfccorp.com/}{https://epfccorp.com/}
  \begin{itemize}
  \item Collaborated with 40 developers and 10 business experts in the \emph{Kanban} framework and \emph{DDD} methodology to explore the domain and boundaries of the \textit{ERP} web application.
  \item Employed the \emph{Clojure} programming language and followed the \emph{TDD} process and \textit{CQRS} principle for 27 \emph{microservices}.
  \item Employed the \textit{Event Sourcing} principle and \textit{Simple Queuing service (SQS)} for interacting the microservices.
  \item Designed 27 databases using \emph{PostgreSQL} and utilized the \emph{JDBC} API to interact with the microservices.
  \item Programmed over 10,000 lines of code using the \emph{pair-programming} technique.
  \end{itemize}
  }
  {Java, Spring Boot, Domain-Driven Design, Test-Driven Development, Clojure, AWS, PostgreSQL, Docker, Microservice, Agile, Kanban, Linux, Pair Programming, Pedestal, Jira, Confluence, Bitbucket, Event Sourcing, CQRS, Behaviour-Driven Development}
  
 \emptySeparator
  
\experience
{}
{Java Developer}
{Radpardaz Razi}
{Kermanshah, Iran. \hspace{190 pt} Jan 2020 - June 2022}
{}
{
\linkedin{radpardaz-razi-b976221b3}
\website{https://raadpardaz.ir/}{https://raadpardaz.ir/}
\begin{itemize}
\item Managed the creation of a sizable \emph{ERP} web app, employing \emph{Spring Boot} to interface with \emph{Apereo CAS} as a client.
\item Formulated protocols (\emph{SAML}, \emph{CAS}, and \emph{OAuth 2.0}) to define secure path to interact services with the \textit{CAS}.
\item Managed users' authentication information, including over 20,000 users, using \emph{OpenLDAP} and \emph{Active Directory}
\item Orchestrated storage of logs, data in \emph{MongoDB}, overseeing processing through \emph{Elastic Search}, involving more than 100 queries.
\end{itemize}
}
{Central Authentication System (CAS), Single Sign in Single Sign out (SSO), Spring Boot, Spring Security, SAML, CAS, OAuth 2.0, Apache Tomcat, Gradle, Hibernate, MongoDB, OpenLDAP, Elastic Search, MVC, REST API, Bash Script, Linux, Scrum}
\emptySeparator
\experience
  {}
  {Android Developer }
  {SPOT online taxi}
  {Kermanshah, Iran. \hspace{140 pt} September 2017 - May 2019}
  {}
  {
  \website{https://www.spotbar.ir/}{https://www.spotbar.ir/} 
  \begin{itemize}
    \item As a member of a mid-size team with fewer than 20 members, actively contributed to the development of an Android online taxi application using Java.
    \item Leveraged the 3 Google service \emph{Geolocation}, \emph{Geocode}, and \emph{Geocode reverse} APIs of the Google Map platform for navigation in the application.
  \end{itemize}
  }
  {Java, Android Studio, JUnit, MVC, JDBC, SQLite, SQL, Google Map Platform}

\emptySeparator

\experience
{}
{Android Developer }
{Islamic Azad University incubator}
{Kermanshah, Iran. \hspace{60 pt} September 2015 - July 2017}
{}
{
\begin{itemize}
\item Collaborated as a JAVA developer with three teams, consisting of over 10 developers, in successfully setting up 3 startups.
Crafted a dual-level cache utilizing the \emph{SharedPreference} API and in-memory \emph{SQLite} database to manage cached information from a \emph{MySQL} database, catering to 1000+ users and entities.\item Built 2 rich social media applications and ensured their API security using the \emph{JWT} token.
\end{itemize}
}
{Java, Android Studio, JUnit, MVC, JDBC, JWT, MySQL, SQLite, cPanel}

\emptySeparator
\end{experiences}