%Section: Project
\sectionTitle{Projects}{\faLaptop}

\begin{projects}
	\project
	{Friendship Recommendation Algorithm}{2017 - 2018}
	{\github{https://github.com/maziyar-gerami/friendship-recommendation}{} {Freelancing} }
	{This project focuses on developing a novel algorithm for friendship recommendation in social networks. The algorithm leverages the analysis of structural and profile-based mutual friends graphs to provide personalized friendship suggestions to users. The goal is to enhance the user experience and foster meaningful connections in the social network.}
	{Matlab, Algorithm, Artificial Intelligence}
				
	\project
	{Improved TDOA-Based Localization Accuracy in Wireless Sensor Networks Using RBF Neural Network}{2017 - 2018}
	{\github{https://github.com/maziyar-gerami/LocatingWSNTDOA}{} {Freelancing} }
	{This project aims to improve the localization accuracy in wireless sensor networks by enhancing the TDOA-based method. We employ Radial Basis Function (RBF) Neural Networks as a novel approach to address the challenges associated with traditional TDOA localization methods.}
	{Matlab, Algorithm, Artificial Intelligence, Neural Networks, Radial Basis Function Neural Networks (RBFNN)}

	\project
	{Community Detection in Social Network}{2016 - 2017}
	{\github{https://github.com/maziyar-gerami/CommunityDetecion}{} {Freelancing} }
	{This project focuses on community detection in social networks, a fundamental task in network analysis. Community detection aims to identify groups of nodes within a network that are more densely connected to each other than to nodes outside of their group. This README provides an overview of the project and how to get started.}
	{Matlab, Algorithm, Artificial Intelligence, Clustering, Kmeans}

	\project
	{Layout Optimization for Wireless Sensor Networks Using Honey Bee Colony Optimization}{2016 - 2017}
	{\github{https://github.com/maziyar-gerami/LayoutOptimiztionWSN}{} {Freelancing} }
	{This project focuses on optimizing the layout of wireless sensor networks (WSNs) using the Honey Bee Colony Optimization (HBCO) algorithm. The primary objective is to find an optimal sensor placement that minimizes energy consumption, maximizes coverage, and enhances the efficiency of the WSN.}
	{Matlab, Algorithm, Artificial Intelligence, Wireless Sensor Network, Optimization, Metaheuristic Algorithm, Honey Bee Colony Optimization (HBCO)}
	
	\project
	{Energy-Efficient Algorithm in Mobile Cloud Computing}{2016 - 2017}
	{\github{https://github.com/maziyar-gerami/reducingEnergyCloud}{} {Freelancing} }
	{This project focuses on proposing a novel energy-efficient algorithm for Mobile Cloud Computing (MCC), an emerging paradigm that integrates mobile devices and cloud computing to enhance performance while conserving energy.}
	{Matlab, Algorithm, Artificial Intelligence, Mobile Cloud Computing}
	\newpage
	\project
	{A Hybrid Bee Colony and Ant Colony Algorithm for Virtual Machine Placement}{2015 - 2016}
	{\github{https://github.com/maziyar-gerami/vm-replacement-ant-bee}{} {Freelancing} }
	{This project focuses on optimizing the placement of virtual machines (VMs) in a cloud data center. Efficient VM placement is crucial for maximizing resource utilization and minimizing operational costs in cloud computing environments. To address this challenge, we have developed a hybrid algorithm that combines the Bee Colony Optimization (BCO) and Ant Colony Optimization (ACO) algorithms.}
	{Matlab, Algorithm, Artificial Intelligence, Mobile Cloud Computing, Bee Colony Optimization (BCO), Ant Colony Optimization (ACO)}

	\project
	{Cloud Computing Scheduling for Big Data Processing Using Memetic Algorithms}{2015 - 2016}
	{\github{https://github.com/maziyar-gerami/cloud-scheduling-memetic}{} {Freelancing} }
	{This project provides a cloud computing scheduling algorithm for efficient processing of Big Data using Memetic Algorithms. The implementation is in Java and utilizes the CloudSim framework for cloud computing simulation. Additionally, the project includes a comparison with the Genetic Algorithm (GA) for performance evaluation.}
	{Java, CloudSim, Artificial Intelligence, Metaheuristic algorithms, Genetic Algorithm (GA)}

	\project
	{Course Timetable Optimization Using Biogeography-Based Optimization (BBO) }{2014 - 2015}
	{\github{https://github.com/maziyar-gerami/timetable-problem-bbo}{} {Freelancing} }
	{Welcome to the Course Timetable Optimization project! This project proposes a decision support system for solving the complex course timetable problem using the Biogeography-Based Optimization (BBO) algorithm implemented in MATLAB. The aim is to efficiently schedule courses, classrooms, and instructors while satisfying various constraints.}
	{Matlab, Algorithm, Artificial Intelligence, Artificial Intelligence, Metaheuristic algorithms, Biogeography-Based Optimization (BBO) algorithm}

\end{projects}