\sectionTitle{Experience}{\faSuitcase}
\begin{experiences}
  \experience{}{Java Software Engineer}{Avan Software Technology Advisors (ASTA)}{Tehran, Iran. \hspace{50 pt} January 2024 - Peresent }{}
{
  Linkedin: \linkedin{avan-soft}
  Website: \website{https://asta.ir/}{https://asta.ir/}\\
  Avan Software Technology Advisors (\emph{ASTA}) was founded in 2003 missions to deliver IT solutions to a wide range of enterprises in public sector services.
  \begin{itemize}
    \item Spearheaded the development of RESTful and microservices-based APIs within the \emph{Flickit} open-source project, leveraging Java 17 and \emph{Spring Boot} technologies.
    \item Implemented Hexagonal Architecture design principles for more than 30 ports and adapters to ensure modularity and scalability in developing APIs, fostering a robust and maintainable codebase.
    \item Collaborated within a midsize team to integrate \emph{Minio} storage solutions, enhancing data management capabilities while adhering to Test-Driven Development (TDD) practices and promoting clean code standards. We utilized \emph{Liquibase} for database schema management and \emph{PostgreSQL} for data storage.  \end{itemize}}
    {Java, Spring Boot, PostgreSQL, MinIO Object Storage, Test-Driven Development, Docker, Microservice, Kubernetes, Scrum, Linux, Jira, Clean Code, Clean Architecture, Hexagonal Architecture, BDD, JUnit, Mockito, Elastic Search, Logstash, Sentry}
 \emptySeparator
 \experience{}{Senior Clojure Developer}{EPFC}{Calgary, Canada. \hspace{180 pt} July 2022 - December 2023 }{}
 {
   Linkedin: \linkedin{epfccorp}
   Website: \website{https://epfccorp.com/}{https://epfccorp.com/}\\
   \emph{EPFC} is a diverse team of professionals with extensive experience in engineering, procurement, fabrication, construction, commission and start-up, and operations in oil and gas. As a part of the IT team, we developed an \emph{ERP} system to facilitate the company procedures.
   \begin{itemize}
   \item Engaged with 50 developers and experts using \emph{Scrum} and \emph{DDD} to investigate the \textit{ERP} web app's domain and boundaries.
   \item Employed the \emph{Clojure} programming language and followed the \emph{TDD} process and \textit{CQRS} principle for 27 \emph{microservices}.
   \item Employed the \textit{Event Sourcing} principle and \textit{Simple Queuing Service (SQS)} for interacting the microservices.
   \item Collaborated with the DevOps team in terms of Automation and Bash Scripting to achieve more than 30 per cent, speeding up the deploying procedure.
   \end{itemize}}{Clojure, Java, Spring Boot, Domain-Driven Design, Test-Driven Development, AWS, PostgreSQL, Docker, Microservice, Agile, Kanban, Linux, Pair Programming, Pedestal, Jira, Confluence, Bitbucket, Event Sourcing, CQRS, BDD, DevOps, CI/CD, Events, Messaging}
  \emptySeparator
\experience
{}
{Java Developer}
{Radpardaz Razi}
{Kermanshah, Iran. \hspace{170 pt} January 2020 - June 2022}
{}
{
Linkedin : \linkedin{radpardaz-razi-b976221b3}
Website \website{https://raadpardaz.ir/}{https://raadpardaz.ir/}
\par{Radpardaz Razi operates within the security IT industry, specializing in enhancing the security of existing applications and developing new ones.}
\begin{itemize}
\item Managed the creation of a sizable \emph{ERP} web app, employing \emph{Spring Boot} to interface with \emph{Apereo CAS} as a client.
\item Formulated protocols (\emph{SAML}, \emph{CAS}, and \emph{OAuth 2.0}) to define a secure path to interact services with the \textit{CAS}.
\item Managed users' authentication information, including over 20,000 users, using \emph{OpenLDAP} and \emph{Active Directory}
\item Orchestrated storage of logs and data in \emph{MongoDB}, overseeing processing through \emph{Elastic Search}, involving more than 100 queries.
\end{itemize}
}{Central Authentication System (CAS), Single Sign in Single Sign out (SSO), Spring Boot, Spring Security, SAML, CAS, OAuth 2.0, Apache Tomcat, Gradle, Hibernate, MongoDB, OpenLDAP, MVC, REST API, Bash Script, Json, Http, Linux, Scrum}
\emptySeparator
\experience
  {}
  {Android Developer}
  {SPOT online taxi}
  {Kermanshah, Iran. \hspace{140 pt} September 2017 - May 2019}
  {}
  {
  Website: \website{https://www.spotbar.ir/}{https://www.spotbar.ir/}\\
  SPOT is a prominent online taxi service with a user base exceeding 100,000 in Iran. 
  \begin{itemize}
    \item In a sub-20 member team, aided Android taxi app development using Java.
    \item Employed Google Map's \emph{Geolocation}, \emph{Geocode}, and \emph{Reverse Geocode} APIs for navigation.\end{itemize}
  }{Java, Android Studio, JUnit, MVC, JDBC, SQLite, SQL, Google Map Platform}

\emptySeparator

\experience
{}
{Android Developer}
{Islamic Azad University incubator}
{Kermanshah, Iran. \hspace{60 pt} September 2015 - July 2017}
{}
{
\begin{itemize}
\item Collaborated as a Java developer with three teams, consisting of over 10 developers, in successfully setting up 3 startups.
\item Crafted a dual-tier cache with \emph{SharedPreference} API and \emph{SQLite} database for 1000+ records from a \emph{MySQL} database.
\item Built 2 rich social media applications and ensured their API security using the \emph{JWT} token.
\end{itemize}
}{Java, Android Studio, JUnit, MVC, JDBC, JWT, MySQL, SQLite, cPanel}
\end{experiences}